Visualizations for the manuscript

### 2022-05-14 metanalysis_visualization/manuscript_Figures.Rmd
update sex proportion figure

df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  left_join(coefficients_df_sex, by = c("sex"))

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Female proportion period differences: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  geom_label(data = plot_annotations_sex_df,
             aes(label = label),
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  annotate("text_female", x = 7, y = 0.85, label = "Female proportion") + 
  annotate("text_male", x = 7, y = 0.15, label = "Male proportion") + 
  labs(title = "Interrupted Time Series Analysis: Patients sex proportion",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))

ggsave("figure4_ITS_sex.png", height = 15, width = 20, units = "cm")
```

>>>>

df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  left_join(observed_coefficients_df_sex, by = c("sex"))

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Female proportion since pandemic coefficient: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.02) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  geom_label(data = plot_annotations_sex_df,
             aes(label = label),
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-08-01'),
           y = 0.69,
           label = "Female proportion", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-08-01'),
           y = 0.3,
           label = "Male proportion", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(title = "Patients sex proportion trends among psychiatric-related visits",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
plot_sex
ggsave(plot = plot_sex, filename = "figure4_ITS_sex.png", height = 15, width = 20, units = "cm")
```
